{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-10 thesis/intro.tex
explain the joke of landslide - pebbles, in intro

\revision{The foundation of this work is Landslide, a stateless model checker
%for thread libraries and kernels that
I have built over the last seven years, first debuting in my M.S. thesis~\cite{landslide}.
Since then, I have extended it with a wide array of features and algorithms,
some from prior work and some of my own devising,
some which work behind the scenes and others which rely on human feedback to be effective,
in pursuit of this thesis statement.

>>>>

\revision{The foundation of this work is Landslide, a stateless model checker
%for thread libraries and kernels that
I have built over the last seven years, first debuting in my M.S. thesis~\cite{landslide},
so named because it tests the stability of Pebbles programs students write in 15-410 at CMU.
Since then, I have extended it with many features and algorithms,
%some from prior work and some of my own devising,
some which work behind the scenes and others which rely on human feedback to be effective,
in pursuit of this thesis statement.
